TacticToe: Learning to Prove with Tactics

### 2018-03-05 tactictoe_jv.tex
replacing support by domain
removing domain
search tree definition
todo

@@

\begin{definition}\label{def:stree}(search tree)\\
A search tree $\mathfrak{T}$ is a sixtuple
$(\mathbb{T},\mathbb{G},\mathbb{A},T,G,A)$
that respects the following conditions:
\begin{itemize}
\item $\mathbb{T}$ is a set of tactics, $\mathbb{G}$ is a set of goals
 and $\mathbb{A}$ is a set of nodes representing lists of goals.
\item $T$ is a function from $\mathbb{G}$ to $\mathcal{P}(\mathbb{T})$. It
takes a goal and return the set of tactics already applied to this goal.
\item $G$ is a total function from $\mathbb{A}$ to $\mathcal{P}(\mathbb{G})$.
It takes a node and returns the list of goals of this node.
\item $A$ is a partial function from $\mathbb{G} \times \mathbb{T}$ to
$\mathbb{A}$. Its support $\mathit{Support}(A)$ is 
$\lbrace (g,t) \in \mathbb{G} \times \mathbb{T}\ |\ t \in T(g)
\rbrace$. And if $(g,t) \in \mathit{Support}(A)$, then $t(g) = G(A(g,t))$. In 
other words, the output $t(g)$ is exactly the list
of goals contained in the node produced by $A$ from $(g,t)$.
\item It is acyclic, i.e. a node cannot be a strict descendant (see 
Definition~\ref{def:desc}) of itself.
\item There is exactly one node with no parents. This root node contains 
exactly one goal which is the initial goal (also called conjecture).
\end{itemize}

@@

\paragraph{Acknowledgments}\label{sect:acks}
We would like to thank Lasse Blaauwbroek for his insightful comments which
contributed to improve the quality of this paper. This work has been supported
by the ERC Consolidator grant no.\ 649043 \textit{AI4REASON} and ERC starting
grant no.\ 714034 \textit{SMART}.

>>>>

\todoi{graphic explaining how each part relate to each other}

@@

\begin{definition}\label{def:stree}(search tree)\\
A search tree $\mathfrak{T}$ is a sixtuple
$(\mathbb{T},\mathbb{G},\mathbb{A},T,G,A)$
that respects the following conditions:
\begin{itemize}
\item $\mathbb{T}$ is a set of tactics, $\mathbb{G}$ is a set of goals
 and $\mathbb{A}$ is a set of nodes representing lists of goals.
\item $T$ is a function from $\mathbb{G}$ to $\mathcal{P}(\mathbb{T})$. It
takes a goal and return the set of tactics already applied to this goal.
\item $G$ is a function from $\mathbb{A}$ to $\mathcal{P}(\mathbb{G})$.
It takes a node and returns the list of goals of this node.
\item $A$ is a function that takes a pair $(g,t)\in \mathbb{G} \times 
\mathbb{T}$ such as $t \in T(g)$ and 
returns a node $A(g,t)$ such as $t(g) = G(A(g,t))$. In other words, the output 
$t(g)$ is exactly the list of goals contained in $A(g,t)$.
\item It is acyclic, i.e. a node cannot be a strict descendant (see 
Definition~\ref{def:desc}) of itself.
\item There is exactly one node with no parents. This root node contains 
exactly one goal which is the initial goal (also called conjecture).
\end{itemize}

@@

\paragraph{Acknowledgments}\label{sect:acks}
We would like to thank Lasse Blaauwbroek and Yutaka Nagashima for their 
insightful comments which
contributed to improve the quality of this paper. This work has been supported
by the ERC Consolidator grant no.\ 649043 \textit{AI4REASON} and ERC starting
grant no.\ 714034 \textit{SMART}.
